\Large {\bf Protocol-Guided Analysis of Post-silicon Traces Under Limited Observability}

### 2015-09-29 paper.tex
updated abstract
the end of introduction is also updated.

Added a paragraph at the beginning of section V to mention the previous
case study.

\begin{abstract}
We consider the problem of reconstructing system-level
behavior of an SoC design from a partially observed signal
trace.  Solving this problem is a critical activity in
post-silicon validation, and currently depends primarily on
human creativity and insight.  We provide algorithms to
automatically infer system-level transactions from
incomplete, ambiguous, and noisy trace data, together with a
measure of confidence.  We demonstrate the approach on
illustrative system-level protocols for SoC models developed
in SystemC as well as in an FPGA environment.
\end{abstract}

@@

In this paper, we consider the problem of reconstructing
protocol-level behavior from silicon traces in SoC designs.
Given a collection of system-level communication protocols
and a trace of (partially observed) hardware signals, our
approach infers, with a certain measure of confidence, the
protocol instances (and their interleavings) being exercised
by the trace.  The approach is based on a formalization of
system-level transactions via labeled Petri-Nets, which are
capable of describing sequencing, concurrency, and choices
over system events.  We develop algorithms to infer
system-level transactions from traces with missing, noisy,
and ambiguous signal values.
% together with an estimate of confidence on the inference.  
We demonstrate our approach on
two SoC case studies: a pedagogical SystemC prototype and a
more realistic implementation constructed within the GEM5
environment~\cite{Binkert2011}.

@@

@@

In order to find out the efficiency of the trace analysis method for more realistic examples, in this case study, a more detailed transaction level model of a SoC is constructed within the GEM5 environment~\cite{Binkert2011}.  This SoC model consists of two ARM Cortex-A9 cores, each of which contains two separate 16KB data and instruction caches.  The caches are connected to a 1GB memory through a memory bus model.  The architecture of this SoC model is shown in Fig.~\ref{SoC}.

>>>>

\begin{abstract}
We consider the problem of reconstructing system-level
behavior of an SoC design from a partially observed signal
trace.  Solving this problem is a critical activity in
post-silicon validation, and currently depends primarily on
human creativity and insights.  In this paper, we provide an algorithm to
automatically infer system-level transactions from
incomplete, ambiguous, and noisy trace data.
% together with a measure of confidence.  
We demonstrate the approach on a multicore virtual platoform
developed within the GEM5 environment.
\end{abstract}

@@

In this paper, we consider the problem of reconstructing
protocol-level behavior from silicon traces in SoC designs.
Given a collection of system-level communication protocols
and a trace of (partially observed) hardware signals, our
approach infers, with a certain measure of confidence, the
protocol instances (and their interleavings) being exercised
by the trace.  The approach is based on a formalization of
system-level transactions via labeled Petri-Nets, which are
capable of describing sequencing, concurrency, and choices
over system events.  We develop algorithms to infer
system-level transactions from traces with missing, noisy,
and ambiguous signal values.
% together with an estimate of confidence on the inference.  
We demonstrate our approach on a multicore virtual platform
constructed within the GEM5 environment~\cite{Binkert2011}.

@@

The proposed method is demonstrated on a transaction level model of a simple SoC design with CPU core, memory, and a peripheral device connected by a highly concurrent interconnect in SystemC.  Since the proposed method is communication centric, the detailed computations of these blocks are not modeled.  Instead, the modeling is focused on how they participate in system level protocols.  This simple case study shows that the proposed method is capable of providing useful information to help reveal and locate various bugs in the SystemC model, thus making the debugging more efficient.  Once a bug-free model is available, the trace analysis method can correctly derive the instances of system flows activated by various components in the design from the observed traces.  More details about the design model and system flows implemented by the design model will be provided in a supplement document stored online.

@@

In order to find out the efficiency of the trace analysis method for more realistic examples, in the case study described in this section, a more detailed transaction level model of a SoC is constructed within the GEM5 environment~\cite{Binkert2011}.  This SoC model consists of two ARM Cortex-A9 cores, each of which contains two separate 16KB data and instruction caches.  The caches are connected to a 1GB memory through a memory bus model.  The architecture of this SoC model is shown in Fig.~\ref{SoC}.
